Microbial interactions as drivers of a chemostat ecosystem

### 2020-01-14 tex/Article_Interactions.tex
Test
Test2
Commentaires et corrections

The classical ecological concept of species and niche in the microbial world is an elusive one: In the macro world one can clearly identify one species of another for reproductive reasons and their ability to give birth to offspring. In the case of bacteria and archea, reproduction goes simply by mitosis and exchange of some functional genes (the ability to synthesize or metabolize substances) can be acquired in evolutionary scale through lateral gene transfer \cite{Boucher2003}. Therefore as an ecological problem is hard to precise the 'niche' of 'species'.

These obstacles can be circumvented by considering the microbiologist concept of operative taxonomic unit (OTU) based in 16sRNA analysis. There is a core genome in Bacteria, which is in turn related to the main metabolism of Bacteria. The abundance of the present OTU allows to account for a group of Bacteria that behave similarly in terms of which substances catabolyzes and at which growth rates and substrate to biomass conversion yields \cite{Muyzer1993}.

@@

The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing technique that can quantify the species abundances through time. This is a first step towards developing predictive models of a reactor's outcome based on the microbial community structure.

@@

The operating diagram from one of the sets of the parameter identification (obtained with a Bayesian estimation method) from Dumont et al. is presented in figure \ref{OD Dumont}. Their fit describes well the dynamics of the OTU, which is not the case for measured chemical species. Two OTU per functional group were considered. One can see that coexistence in the same functional group is never attained. However when using a different set of parameters one can see a more complex situation where coexistence in the same functional group is possible as seen in figure \ref{OD modified}. In the latter case CN can be achieved at a more elevated dilution rats than in the former case. Parameters of cases 1 and 2 can be seen in table \ref{Parameters Dumont} and \ref{Parameters Modified}, respectively.

@@

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{Interactions_Parameters_Dumont}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
	\includegraphics[width=\textwidth]{OD_parameters_Dumont}
	\end{subfigure}
	\caption{Left: interactions of the system. Right: operating diagram of Model \eqref{system}, with parameters in Table \ref{Parameters Dumont}. The different zones represent the surviving species in the steady state. PN takes place when neither $x_3$ nor $x_4$ are present. CN takes place if $x_3$ or $x_4$ are present.}
	\label{OD Dumont}
\end{figure}

\begin{table}[ht]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		Modified Parameters  & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
		$x_1 \in G_1$ &0.828  &0.147  & 5 \\ \hline
		$x_2\in G_1$ & 0.621 & 0.0147 & 3 \\ \hline
		$x_3\in G_2$ & 0.18 & 0.026 & 110 \\ \hline
		$x_4\in G_2$ & 0.135& 0.0026& 90 \\ \hline
	\end{tabular}
	\caption{Kinetic parameters of model \eqref{system} modified from \cite{Dumont2016}.}
	\label{Parameters Modified}
\end{table}
\begin{figure}[ht]
	\centering	
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{Interactions_Parameters_modifed}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{OD_parameters_modified}
	\end{subfigure}
	\caption{Left: interactions of the system. Right: operating diagram of Model \eqref{system}, with parameters in Table \ref{Parameters Modified}. The 8 different zones represent the surviving species in the steady state. PN takes place when neither $x_3$ nor $x_4$ are present. CN takes place if $x_3$ or $x_4$ are present.}
	\label{OD modified}
\end{figure}
\clearpage

@@

More generally the interaction function is defined. It represents how the growth rate of species $i$ is affected by the concentration of other species, $x$:

@@

Figures \ref{Total Biomass no noise}, \ref{AOB no noise}, and \ref{NOB no noise} show the total biomass concentration, and the trajectories for the OTU belonging to $G_1$ and $G_2$, respectively. It can be seen that the method approaches well the trajectories. The metabolites concentration represented in figure \ref{Metabolites no noise} are in accordance with the simulated: The method is able to reconstruct the metabolites trajectories from the community measurements. 
\begin{figure}[h]
	\centering	
	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
	\caption{Interaction Matrix of the synthetic data.}
	\label{Interaction Matrix Simulation}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_Biomass_Iter_10}
	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{Total Biomass no noise}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_AOB_Iter_10}
	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{AOB no noise}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_NOB_Iter_10}
	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{NOB no noise}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_metabolites_Iter_10}
	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{Metabolites no noise}
\end{figure}
\clearpage

@@

The method was stopped after 10 iterations where each iteration took approximately 800 seconds of computing time in a computer equipped with 8gb of RAM memory and Intel core i3-7100U CPU 2,40 GHz.

The tracking problem was applied to data coming from a nitrification process; the experimental conditions are described in \cite{dumont2008observers}. For exploring the hypothesis of interactions as drivers of bioreactors performance environmental conditions should be kept as constant as possible. Therefore only data from day $183$ onwards was used because a change in the operating temperature happened at that point, which is known to have an effect on the kinetics. For choosing which species belong in which functional group, the procedure described in \cite{Ugalde-Salas2019} was used: from day $183$ to day $315$: 30 OTU were identified in the $G_1$ group (known as Ammonium oxidizing bacteria AOB) and 5 in the $G_2$ functional group (known as Nitrite oxidizing bacteria NOB). The system state dimension becomes 38.

The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}. Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$. 
\begin{align}
\label{monod} f_i(s) &= \bar{\mu}_2 \dfrac{s_1}{K_1 +s_1} \, \forall i \in G_1 \\
\notag  f_i(s) &= \bar{\mu}_2 \dfrac{s_2}{K_2 +s_2 } \, \forall i \in G_2
\end{align}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_NOB_Iter_0}
	\caption{Simulation when $u=1$. }
	\label{u=1_NOB}
\end{figure}
\pagebreak
When applying the presented method one obtains the simulation that can be seen in figure \ref{ControlSimulation}. The method captures the tendencies in the measured substrates. The simulation of each functional $G_1$ (AOB), and $G_2$ (NOB) can be seen in figures \ref{AOBSimulation} and \ref{NOB Simulation}, respectively. Note that the fit of $G_1$ seems better than the fit of $G_2$, which can be explained by the 1 order of magnitude difference of abundance between the members of the group.

@@

The interaction function introduced tries to address the issue of prediction from genetic sequencing. The analysis of the gLV model proposed by Dumont \textit{et al.} \cite{Dumont2016} shows a new mechanism by which the CEP may not hold, however we conjecture that the system seems to have only one positive stable equilibrium. From the application section one can see that by correcting the growth rate one is able to recuperate the chemical species dynamics, implying that interactions are driving the system. The former correction varies strongly and when compared to the proof of section one may hypothesise that linear pairwise interaction model can not capture the complexity of the particular chemostat analysed. This opens the question for a broader class of interaction functions that could fit well complex microbial ecosystems. The experimental study in chemostat systems seems a good compromise between completely open ecosystems (nature) and controlled conditions (laboratory) in order to explore expressions that could account for microbial interactions.

>>>>

The classical ecological concept of species and niche in the microbial world is an elusive one: In the macro world one can clearly identify one species of another for reproductive reasons and their ability to give birth to offspring. In the case of bacteria and archea, reproduction goes simply by binary fission and exchange of some functional genes (the ability to synthesize or metabolize substances) can be acquired in evolutionary scale through lateral gene transfer \cite{Boucher2003}. Therefore as an ecological problem is hard to precise the 'niche' of 'species'.

These obstacles can be circumvented by considering the microbiologist concept of operative taxonomic unit (OTU) based on the clustering of organisms sharing similar sequences of 16S rDNA marker gene. There is a core genome in Bacteria, which is in turn related to the main metabolism of Bacteria\iffalse cette phrase n'est pas claire, on pourrait éventuellement simplement la retirer \fi. The abundance of the present OTU allows to account for a group of Bacteria that behave similarly in terms of which substances catabolyzes and at which growth rates and substrate to biomass conversion yields \cite{Muyzer1993}.

@@

The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing or fingerprinting technique that can quantify the species abundances through time. This is a first step towards developing predictive models of a reactor's outcome based on the microbial community structure.

@@

The operating diagram from one of the sets of the parameter identification (obtained with a Bayesian estimation method) from Dumont et al. is presented in figure \ref{OD Dumont}. Their fit describes well the dynamics of the OTU, which is not the case for measured chemical species. Two OTU per functional group were considered. One can see that coexistence in the same functional group is never attained. However when using a different set of parameters one can see a more complex situation where coexistence in the same functional group is possible as seen in figure \ref{OD modified}. In the latter case CN can be achieved at a more elevated dilution rate than in the former case. Parameters of cases 1 and 2 can be seen in table \ref{Parameters Dumont} and \ref{Parameters Modified}, respectively.

@@

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{Interactions_Parameters_Dumont}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
	\includegraphics[width=\textwidth]{OD_parameters_Dumont}
	\end{subfigure}
	\caption{Left: interaction matrix associated with model \eqref{system} as estimated in Dumont el al. \cite{Dumont2016} for a consortia of 4 bacterial species where $x_1$ and $x_2$ are AOB and $x_3$ and $x_4$ are NOB. Right: associated operating diagram with parameters in Table \ref{Parameters Dumont}. The different zones represent the surviving species in the steady state. PN takes place when neither $x_3$ nor $x_4$ are present. CN takes place if $x_3$ or $x_4$ are present.}
	\label{OD Dumont}
\end{figure}

\begin{table}[ht]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		Modified Parameters  & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
		$x_1 \in G_1$ &0.828  &0.147  & 5 \\ \hline
		$x_2\in G_1$ & 0.621 & 0.0147 & 3 \\ \hline
		$x_3\in G_2$ & 0.18 & 0.026 & 110 \\ \hline
		$x_4\in G_2$ & 0.135& 0.0026& 90 \\ \hline
	\end{tabular}
	\caption{Kinetic parameters of model \eqref{system} modified from \cite{Dumont2016}.}
	\label{Parameters Modified}
\end{table}
\begin{figure}[ht]
	\centering	
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{Interactions_Parameters_modifed}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{OD_parameters_modified}
	\end{subfigure}
	\caption{Left: random interaction matrix associated with model \eqref{system} for a consortia of 4 bacterial species where $x_1$ and $x_2$ are AOB and $x_3$ and $x_4$ are NOB. Right: associated operating diagram with parameters in Table \ref{Parameters Modified}. The 8 different zones represent the surviving species in the steady state. PN takes place when neither $x_3$ nor $x_4$ are present. CN takes place if $x_3$ or $x_4$ are present.}
	\label{OD modified}
\end{figure}
\clearpage

@@

More generally the interaction function represents how the growth rate of species $i$ is affected by the concentration of other species, $x$:

@@

Figures \ref{Total Biomass no noise}, \ref{AOB no noise}, and \ref{NOB no noise} show the total biomass concentration, and the trajectories for the OTU belonging to $G_1$ and $G_2$, respectively. It can be seen that the method approaches well the trajectories. The metabolites concentration represented in figure \ref{Metabolites no noise} are in accordance with the simulated: The method is able to reconstruct the metabolites trajectories from the community measurements. 
\begin{figure}[h]
	\centering	
	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
	\caption{Interaction matrix associated with model \eqref{system} for a simulated consortia of 15 bacterial species where $x_1$-$x_{10}$ are AOB and $x_{11}$-$x_{15}$ are NOB.}
	\label{Interaction Matrix Simulation}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_Biomass_Iter_10}
	\caption{Dotted line: simulated total biomass for model \eqref{system} with interactions shown in Figure \ref{Interaction Matrix Simulation} and parameters\iffalse quels paramètres ?\fi. Continuous line: total biomass as predicted  by the tracking procedure.}
	\label{Total Biomass no noise}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_AOB_Iter_10}
	\caption{Dotted line: simulated AOB biomass. Continuous line: the tracking procedure results.}
	\label{AOB no noise}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_NOB_Iter_10}
	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{NOB no noise}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_metabolites_Iter_10}
	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
	\label{Metabolites no noise}
\end{figure}
\clearpage

@@

The method was stopped after 10 iterations where each iteration took approximately 800 seconds of computing time in a computer equipped with 8gb of RAM memory and Intel core i3-7100U CPU 2,40 GHz.\iffalse Cette phrase devrait figurer dans la partie précédente ?\fi

The tracking problem was applied to data coming from a nitrification process; the experimental conditions are described in \cite{dumont2008observers}. For exploring the hypothesis of interactions as drivers of bioreactors performance environmental conditions should be kept as constant as possible. Therefore only data from day $183$ onwards was used because a change in the operating temperature happened at that point, which is known to have an effect on the kinetics. For choosing which species belong in which functional group, the procedure described in \cite{Ugalde-Salas2019} was used: from day $183$ to day $315$: 30 OTU were identified in the $G_1$ group (AOB) and 5 in the $G_2$ functional group (NOB). The system state dimension becomes 38.

The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}\iffalse est-ce que tu donnes les paramètres quelquepart ?\fi. Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$. 
\begin{align}
\label{monod} f_i(s) &= \bar{\mu}_2 \dfrac{s_1}{K_1 +s_1} \, \forall i \in G_1 \\
\notag  f_i(s) &= \bar{\mu}_2 \dfrac{s_2}{K_2 +s_2 } \, \forall i \in G_2
\end{align}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_NOB_Iter_0}
	\caption{Simulation when $u=1$. }
	\label{u=1_NOB}
\end{figure}
\pagebreak
When applying the presented method one obtains the simulation that can be seen in figure \ref{ControlSimulation}. The method captures the tendencies in the measured substrates and products. The simulation of each functional $G_1$ (AOB), and $G_2$ (NOB) can be seen in figures \ref{AOBSimulation} and \ref{NOB Simulation}, respectively. Note that the fit of $G_1$ seems better than the fit of $G_2$, which can be explained by the 1 order of magnitude difference of abundance between the members of the group.

@@

The interaction function introduced tries to address the issue of prediction from genetic sequencing. The analysis of the gLV model proposed by Dumont \textit{et al.} \cite{Dumont2016} shows a new mechanism by which the CEP may not hold, however we conjecture that the system seems to have only one positive stable equilibrium. From the application section one can see that by correcting the growth rate one is able to recuperate the chemical species dynamics, implying that interactions are driving the system. The former correction varies strongly and when compared to the proof of section one may hypothesise that linear pairwise interaction model such as the gLV model can not capture the complexity of the particular chemostat analysed. This opens the question for a broader class of interaction functions that could fit well complex microbial ecosystems. The experimental study in chemostat systems seems a good compromise between completely open ecosystems (nature) and controlled conditions (laboratory) in order to explore expressions that could account for microbial interactions.
